Molecular Analysis

### 2023-10-16 analysis/aud_analysis.Rmd
update plots

# weekly coughs per min by class and condition
coughs_pl <- coughs %>%
  mutate(week = isoweek(date)) %>%
  filter(week != 6) %>%
  mutate(week = ifelse(week < 6, week - min(week) + 1, week - min(week))) %>%
  group_by(class, week) %>%
  summarize(coughs_per_min = sum(n_coughs) / sum(TT),
            aircleaner = first(aircleaner)) %>%
  ungroup() %>%
  mutate(aircleaner = factor(aircleaner, levels = c("Yes", "No")),
         class = factor(class, levels = c("A", "B"))) %>%
  arrange(class, aircleaner) %>%
  ggplot(aes(x = factor(week), y = coughs_per_min, fill = aircleaner, pattern = class)) +
  geom_bar_pattern(stat = "identity", color = "black", pattern_fill = "white", pattern_angle = 45,
                   pattern_density = 0.25, pattern_spacing = 0.05, width = .5) +
  labs(x = "Study week", y = "Number of coughs per min", fill = "Air cleaner", pattern = "Class", title = "a") +
  scale_fill_manual(values = rev(wes_palette("Royal1")[1:2])) +
  scale_x_discrete(breaks = 1:7) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.05)), breaks = seq(0, 10, 2)) +
  scale_pattern_manual(values = c(A = "stripe", B = "none")) +
  theme_custom() +
  theme(legend.position = "top",
        legend.direction = "horizontal",
        legend.key.width = unit(0.5, "cm"),
        legend.key.height = unit(0.3, "cm"),
        plot.title.position = "plot") +
  guides(fill = guide_legend(nrow = 1, override.aes = list(pattern = "none", order = 2)),
         pattern = guide_legend(nrow = 1, override.aes = list(fill = "white"), order = 1))

@@

save_plot(coughs_pl, pdf_file = "../results/cough-data/coughs-frequency-per-week.pdf", eps_file = "../results/cough-data/coughs-frequency-per-week.eps", w = 12, h = 8)
```

@@

theta_pl <- draws_theta %>%
  ggplot(aes(y = v, x = rr, color = v)) +
  geom_vline(aes(xintercept = 1), linetype = "dotted", color = "red") +
  stat_pointinterval(shape = 21, fill = "white") +
  scale_color_manual(values = wes_palette("IsleofDogs1")) +
  labs(x = "Relative risk", title = "b") +
  theme_custom() +
  theme(axis.title.y = element_blank(), legend.position = "none",
        plot.title.position = "plot")

theta_pl
save_plot(theta_pl, pdf_file = "../results/cough-data/coughs-virus-association.pdf", eps_file = "../results/cough-data/coughs-virus-association.eps", w = 12, h = 8)
```

>>>>

# weekly coughs per min by class and condition
coughs_pl <- coughs %>%
  group_by(aircleaner) %>%
  summarize(coughs_per_min = sum(n_coughs) / sum(TT)) %>%
  ungroup() %>%
  mutate(aircleaner = factor(aircleaner, levels = c("No", "Yes"))) %>%
  ggplot(aes(x = aircleaner, y = coughs_per_min, fill = aircleaner)) +
  geom_bar(stat = "identity", color = "black") +
  geom_text(mapping = aes(label = round(coughs_per_min, 1)),
            size = 8 / cm(1), vjust = -1) +
  labs(x = "Study week", y = "Number of coughs per min", fill = "Air cleaner", title = "d") +
  scale_fill_manual(values = wes_palette("Royal1")[1:2]) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
  theme_custom() +
  theme(legend.position = "none",
        legend.direction = "horizontal",
        legend.key.width = unit(0.5, "cm"),
        legend.key.height = unit(0.3, "cm"),
        plot.title.position = "plot") +
  guides(fill = "none")

@@

save_plot(coughs_pl, 
          pdf_file = "../results/cough-data/coughs-frequency-by-condition.pdf", 
          eps_file = "../results/cough-data/coughs-frequency-by-condition.eps", 
          w = 8, h = 8)
```

@@

theta_pl <- draws_theta %>%
  ggplot(aes(y = v, x = rr, color = v)) +
  geom_vline(aes(xintercept = 1), linetype = "dotted", color = "red") +
  stat_pointinterval(shape = 21, fill = "white") +
  scale_color_manual(values = wes_palette("IsleofDogs1")) +
  labs(x = "Relative risk") +
  theme_custom() +
  theme(axis.title.y = element_blank(), legend.position = "none",
        plot.title.position = "plot")

theta_pl

save_plot(theta_pl, 
          pdf_file = "../results/cough-data/coughs-virus-association.pdf", 
          eps_file = "../results/cough-data/coughs-virus-association.eps", 
          w = 12, h = 8)
```

### 2023-10-16 analysis/env_analysis.Rmd
update network plot with air and filter samples
update plots

@@

```{r}
# particle concentrations
boxpl_pc <- env_epi_data %>%
  dplyr::select(class, date, weekday, aircleaner, Cn, PM1, PM25, PM4, PM10) %>%
  melt(c("class", "date", "weekday", "aircleaner")) %>%
  rename(`Air Cleaner` = aircleaner,
         Class = class) %>%
  ggplot(aes(x = `Air Cleaner`, color = `Air Cleaner`, y = value)) +
  facet_wrap(~ variable, scales = "free_y", nrow = 1, dir = "h", labeller = as_labeller(vars_labels, label_parsed)) +
  geom_boxplot2() +
  geom_jitter(aes(shape = Class), alpha = .3, width = .2) +
  scale_color_manual(values = wes_palette("Royal1")) +
  scale_shape_manual(values = c(2,20)) +
  labs(title = "a") +
  theme_custom() +
  theme(axis.title.y = element_blank(), legend.position = "top",
        plot.title.position = "plot") +
  guides(color = "none")
save_plot(boxpl_pc, pdf_file = "../results/env-data/particles-boxplot.pdf", eps_file = "../results/env-data/particles-boxplot.eps", w = 16, h = 8)
saveRDS(boxpl_pc, file = "../results/env-data/particles-boxplot.rds")

>>>>

tt_co2 <- t.test(env_epi_data$CO2[env_epi_data$aircleaner=="Yes"], env_epi_data$CO2[env_epi_data$aircleaner=="No"])

@@

```{r}
# only particle number concentration
boxpl_cn <- env_epi_data %>%
  dplyr::select(class, date, aircleaner, Cn) %>%
  ggplot(aes(x = aircleaner, fill = aircleaner, y = Cn)) +
  geom_boxplot2() +
  #geom_jitter(alpha = .3, width = .2, color = "grey") +
  scale_fill_manual(values = wes_palette("Royal1")) +
  scale_shape_manual(values = c(2,20)) +
  scale_y_continuous(expand = c(0,0), limits = c(0, NA)) +
  labs(title = "b", y = expression("Aerosol number concentration (1/cm"^3*")"), x = "Air cleaner") +
  theme_custom() +
  theme(legend.position = "none",
        plot.title.position = "plot") +
  guides(color = "none")

boxpl_cn

save_plot(boxpl_cn, 
          pdf_file = "../results/env-data/aerosol-number-boxplot.pdf", 
          eps_file = "../results/env-data/aerosol-number-boxplot.eps", 
          w = 8, h = 8)
```

```{r}
# particle concentrations
boxpl_pc <- env_epi_data %>%
  dplyr::select(class, date, weekday, aircleaner, Cn, PM1, PM25, PM4, PM10) %>%
  melt(c("class", "date", "weekday", "aircleaner")) %>%
  rename(`Air Cleaner` = aircleaner,
         Class = class) %>%
  ggplot(aes(x = `Air Cleaner`, color = `Air Cleaner`, y = value)) +
  facet_wrap(~ variable, scales = "free_y", nrow = 1, dir = "h", labeller = as_labeller(vars_labels, label_parsed)) +
  geom_boxplot2() +
  geom_jitter(aes(shape = Class), alpha = .3, width = .2) +
  scale_color_manual(values = wes_palette("Royal1")) +
  scale_shape_manual(values = c(2,20)) +
  labs(title = "a") +
  theme_custom() +
  theme(axis.title.y = element_blank(), legend.position = "top",
        plot.title.position = "plot") +
  guides(color = "none")

save_plot(boxpl_pc, pdf_file = "../results/env-data/particles-boxplot.pdf", eps_file = "../results/env-data/particles-boxplot.eps", w = 16, h = 8)
saveRDS(boxpl_pc, file = "../results/env-data/particles-boxplot.rds")

### 2023-10-16 analysis/epi_analysis.Rmd
update plots

# number of cases by week
cases_by_week_pl <- epi_data %>%
  group_by(class, aircleaner) %>%
  summarize(cases = sum(new_cases)) %>%
  ungroup() %>%
  mutate(aircleaner = factor(aircleaner, levels = c("No", "Yes")),
         class = factor(class, levels = c("A", "B"))) %>%
  arrange(class, aircleaner) %>%
  ggplot(aes(x = aircleaner, y = cases, fill = aircleaner)) +
  geom_bar_pattern(mapping = aes(pattern = class),
                   stat = "identity", color = "black", pattern_fill = "white", pattern_angle = 45,
                   pattern_density = 0.25, pattern_spacing = 0.05, width = .5) +
  geom_text(data = epi_data %>% group_by(aircleaner) %>% summarize(cases = sum(new_cases)) %>% ungroup(),
            mapping = aes(label = cases),
            size = 8 / cm(1), vjust = -1) +
  labs(x = "Air cleaner", y = "Number of cases", fill = "Air cleaner", pattern = "Class", title = "a") +
  scale_fill_manual(values = wes_palette("Royal1")[1:2]) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1)), breaks = scales::pretty_breaks(4)) +
  scale_pattern_manual(values = c(A = "stripe", B = "none")) +
  theme_custom() +
  theme(legend.position = "top",
        legend.box = "horizontal",
        legend.direction = "horizontal",
        legend.key.width = unit(0.5, "cm"),
        legend.key.height = unit(0.3, "cm"),
        plot.title.position = "plot") +
  guides(fill = "none",
         pattern = guide_legend(nrow = 1, override.aes = list(fill = "white"), order = 1))

cases_by_week_pl

save_plot(cases_by_week_pl,
          pdf_file = "../results/epi-data/cases_by_condition.pdf",
          eps_file = "../results/epi-data/cases_by_condition.eps",
          w = 6, h = 8) 
```

@@

avoid_infections_pl <- avoid_infections  %>%
  ggplot() +
  geom_rect(aes(xmin = .lower, xmax = .upper, ymin = 7.5, ymax = 12.5, fill = `.width`)) +
  geom_segment(aes(x = infections, xend = infections, y = 7.5, yend = 12.5), size = 1.5 / cm(1)) +
  geom_point(aes(x = infections, y = 10), size = 3, fill = "white", shape = 21) +
  facet_wrap(~ type, ncol = 1) +
  scale_fill_manual(values = wes_palette("Royal1")[c(3,4,2)]) +
  scale_y_continuous(expand = expansion(mult = c(0.25, 0.25))) +
  scale_x_continuous(limits = c(0, NA), expand = expansion(mult = c(0, 0)), breaks = seq(0, 200, 25)) +
  labs(x = "Estimated number of infections", y = "Scenario", fill = "CrI", title = "b") +
  theme_custom() +
  theme(axis.title.y = element_text(color = "white"),
        axis.text.y = element_text(color = "white"),
        axis.ticks.y = element_blank(),
        legend.position = "top", legend.direction = "horizontal",
        legend.key.height = unit(.25, "cm"), legend.key.width = unit(.35, "cm"), 
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        plot.title.position = "plot",
        panel.spacing = unit(20, units = "pt"),
        strip.text.x = element_text(margin = margin(b = 5)))

save_plot(avoid_infections_pl, 
          pdf_file = "../results/epi-data/avoided-infections.pdf",
          eps_file = "../results/epi-data/avoided_infections.eps",
          w = 10, h = 8)
```

>>>>

# number of cases by week
cases_by_cond_pl <- epi_data %>%
  group_by(aircleaner) %>%
  summarize(cases = sum(new_cases)) %>%
  ungroup() %>%
  mutate(aircleaner = factor(aircleaner, levels = c("No", "Yes"))) %>%
  ggplot(aes(x = aircleaner, y = cases, fill = aircleaner)) +
  geom_bar(stat = "identity", color = "black") +
  geom_text(mapping = aes(label = cases),
            size = 8 / cm(1), vjust = -1) +
  labs(x = "Air cleaner", y = "Number of cases", fill = "Air cleaner", title = "c") +
  scale_fill_manual(values = wes_palette("Royal1")[1:2]) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1)), breaks = scales::pretty_breaks(4)) +
  theme_custom() +
  theme(plot.title.position = "plot") +
  guides(fill = "none")

cases_by_cond_pl

save_plot(cases_by_cond_pl,
          pdf_file = "../results/epi-data/cases_by_condition.pdf",
          eps_file = "../results/epi-data/cases_by_condition.eps",
          w = 8, h = 8) 
```

@@

avoid_infections_pl <- avoid_infections  %>%
  ggplot() +
  geom_rect(aes(xmin = .lower, xmax = .upper, ymin = 7.5, ymax = 12.5, fill = `.width`)) +
  geom_segment(aes(x = infections, xend = infections, y = 7.5, yend = 12.5), size = 1.5 / cm(1)) +
  geom_point(aes(x = infections, y = 10), size = 3, fill = "white", shape = 21) +
  facet_wrap(~ type, ncol = 1) +
  scale_fill_manual(values = wes_palette("Royal1")[c(3,4,2)]) +
  scale_y_continuous(expand = expansion(mult = c(0.25, 0.25))) +
  scale_x_continuous(limits = c(0, NA), expand = expansion(mult = c(0, 0)), breaks = seq(0, 200, 25)) +
  labs(x = "Estimated number of infections", y = "Scenario", fill = "CrI") +
  theme_custom() +
  theme(axis.title.y = element_text(color = "white"),
        axis.text.y = element_text(color = "white"),
        axis.ticks.y = element_blank(),
        legend.position = "top", legend.direction = "horizontal",
        legend.key.height = unit(.25, "cm"), legend.key.width = unit(.35, "cm"), 
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        plot.title.position = "plot",
        panel.spacing = unit(20, units = "pt"),
        strip.text.x = element_text(margin = margin(b = 5)))

save_plot(avoid_infections_pl, 
          pdf_file = "../results/epi-data/avoided-infections.pdf",
          eps_file = "../results/epi-data/avoided_infections.eps",
          w = 12, h = 8)
```

### 2023-10-16 analysis/mol_analysis.Rmd
update plots

```{r}
# positive samples by study condition and week
df_pos <- df %>%
  mutate(week = week(date),
         week = week - min(week) + 1,
         week = ifelse(week > 4, week - 1, week)) %>%
  dplyr::select(aircleaner, week, class, AdV, `Flu B`, HRV, MPV, PIV, `SARS-CoV-2`) %>%
  melt(c("aircleaner", "week", "class")) %>%
  group_by(aircleaner, class, week, variable) %>%
  summarize(n = sum(value)) %>%
  ungroup() %>%
  mutate(variable = as.character(variable), 
         variable = ifelse(variable == "SARS-CoV-2", "CoV", variable),
         variable = factor(variable, levels = c("Flu B", "HRV", "AdV", "CoV", "MPV", "PIV")),
         class = paste("Class", class)) %>%
  arrange(class, week, desc(variable))

pos_week_pl <- ggplot(mapping = aes(x = week, y = n)) +
  facet_wrap(~ class) +
  geom_bar(data = df_pos, mapping = aes(fill = variable),
           stat = "identity", position = "stack") +
  geom_text(data = subset(df_pos, n > 0), mapping = aes(label = n), 
            size = 8 / cm(1), position = position_stack(vjust = 0.5), color = "white") +
  geom_text(
    data = data.frame(class = c("Class A", "Class B"), axis_title = c("Study week", "Study week")),
    mapping = aes(label = axis_title), hjust = 0.5, vjust = 3.5,
    x = min(df_pos$week) + diff(range(df_pos$week)) / 2,
    y = -Inf, color = 'black', size = 8 / cm(1)
  ) +
  scale_fill_manual(values = wes_palette("IsleofDogs1")) +
  scale_y_continuous(expand = expansion(add = c(0,1)), breaks = scales::breaks_width(2)) +
  scale_x_continuous(breaks = seq(1, 7, 1)) +
  labs(y = "Number of positive samples", x = "Study week", fill = "Virus", title = "c") +
  theme_custom() +
  coord_cartesian(clip = "off") +
  theme(panel.grid = element_blank(),
        panel.spacing.x = unit(1, "cm"),
        axis.title.x = element_text(color = "white"),
        legend.position = "none",
        plot.title.position = "plot") +
  guides(fill = guide_legend(nrow = 1))
pos_week_pl
```

```{r}
# positive samples by study condition
df_pos_stud <- df_pos %>%
  group_by(aircleaner, variable) %>%
  summarize(n = sum(n)) %>%
  ungroup()
pos_cond_pl <- ggplot(mapping = aes(x = aircleaner, y = n, fill = variable)) +
  geom_bar(data = df_pos_stud, stat = "identity", position = "stack") +
  geom_text(data = subset(df_pos_stud, n != 0), mapping = aes(label = n), 
            size = 8 / cm(1), position = position_stack(vjust = 0.5), color = "white") +
  scale_fill_manual(values = wes_palette("IsleofDogs1")) +
  scale_y_continuous(expand = c(0,0)) +
  labs(y = "Number of positive samples", x = "Air cleaner", fill = "Virus", title = "b") +
  theme_custom() +
  theme(panel.grid = element_blank(),
        legend.position = "bottom",
        plot.title.position = "plot") +
  guides(fill = guide_legend(nrow = 1))
pos_cond_pl
```

@@

pos_tot_pl <- df_pos_tot %>%
  ggplot(aes(x = variable, y = n, fill = variable)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, y = n + 1), size = 8 / cm(1)) +
  scale_fill_manual(values = wes_palette("IsleofDogs1")) +
  scale_y_continuous(expand = expansion(add = c(0,1))) +
  labs(y = "Number of positive samples", x = "Virus", fill = "Virus", title = "a") +
  theme_custom() +
  theme(panel.grid = element_blank(),
        legend.position = "bottom",
        plot.title.position = "plot") +
  guides(fill = guide_legend(nrow = 1))
pos_tot_pl
```

```{r}
# combine
descr <- pos_tot_pl + plot_spacer() + pos_cond_pl & theme(legend.position = "bottom", legend.key.height = unit(.1, "cm"),
                                          legend.key.width = unit(.3, "cm"))
descr <- descr + plot_layout(guides = "collect", widths = c(9.5, 1, 5.5), ncol = 2) 
descr <- descr + pos_week_pl 
descr <- descr + plot_layout(nrow = 2, heights = c(8, 8), design = 'ABC
                             DDD')
save_plot(descr, pdf_file = "../results/mol-data/descriptives.pdf", eps_file = "../results/mol-data/descriptives.eps", h = 16, w = 16)
# saveRDS(pos_tot_pl + ggtitle(""), file = "../results/mol-data/descriptives-total.rds")
# saveRDS(pos_cond_pl + ggtitle(""), file = "../results/mol-data/descriptives-cond.rds")
# saveRDS(pos_week_pl + ggtitle(""), file = "../results/mol-data/descriptives-week.rds")
```

@@

tnet_pl <- tnet %>%
  mutate(type = factor("Saliva", levels = c("Saliva", "Air", "Filter"))) %>%
  ggplot(aes(y = date_infection, x = virus, size = n, shape = type)) +
  facet_wrap(~ class, ncol = 2, scales = "free_x") +
  ggh4x::facetted_pos_scales(x = mirror_scales) +
  geom_point(data = air_samples %>% 
               mutate(date_infection = as.POSIXct(paste0(date, "00:00:00", format = "%d-%m-%Y %H:%M:%S")),
                      n = factor(1, levels = c(1,2,3)),
                      class = factor(paste("Class", class), levels = c("Class A", "Class B")),
                      type = factor(type, levels = c("Saliva", "Air", "Filter")),
                      virus = factor(virus, levels = c("Flu B", "HRV", "AdV", "CoV", "MPV", "PIV"))),
             mapping = aes(color = virus), fill = "white",
             position = position_dodge(width = -.6, preserve = "single")) +
  geom_point(mapping = aes(fill = virus), color = "black") +
  geom_segment(aes(y = from, yend = to, xend = virus), size = 1,
              arrow = arrow(length = unit(0.2, "cm")), color = "black") +
  labs(size = "Number of infections", fill = "Virus", shape = "") +
  coord_y_datetime(ylim = c(max(tnet$date_infection), min(tnet$date_infection))) +
  scale_y_datetime(date_breaks = "1 week", date_labels = "%b %d") +
  scale_size_discrete(range = c(4,8)) +
  scale_fill_manual(values = wes_palette("IsleofDogs1")) +
  scale_color_manual(values = wes_palette("IsleofDogs1")) +
  scale_shape_manual(values = c("Saliva" = 21, "Air" = 22, "Filter" = 23),
                     breaks = c("Saliva", "Air", "Filter")) +
  theme_custom() +
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box = "horizontal",
        #plot.title.position = "plot",
        axis.title = element_blank(),
        #axis.text.x = element_blank(),
        #axis.ticks.x = element_blank(),
        panel.spacing = unit(1, "cm"),
        panel.grid.major.x = element_line(),
        panel.grid.minor.y = element_blank(),
        strip.text.x = element_text(size = 10, margin = margin(b = 10))) +
  guides(fill = "none",
         color = "none",
         shape = guide_legend(order = 1),
         size = guide_legend(nrow = 1, order = 2))

save_plot(tnet_pl, pdf_file = "../results/mol-data/network-plot.pdf", eps_file = "../results/mol-data/network-plot.eps", w = 16, h = 21)
```

>>>>

```{r}
# positive samples by study condition and week
df_pos <- df %>%
  mutate(week = week(date),
         week = week - min(week) + 1,
         week = ifelse(week > 4, week - 1, week)) %>%
  dplyr::select(aircleaner, week, class, AdV, `Flu B`, HRV, MPV, PIV, `SARS-CoV-2`) %>%
  melt(c("aircleaner", "week", "class")) %>%
  group_by(aircleaner, class, week, variable) %>%
  summarize(n = sum(value)) %>%
  ungroup() %>%
  mutate(variable = as.character(variable), 
         variable = ifelse(variable == "SARS-CoV-2", "CoV", variable),
         variable = factor(variable, levels = c("Flu B", "HRV", "AdV", "CoV", "MPV", "PIV")),
         class = paste("Class", class)) %>%
  arrange(class, week, desc(variable))
```

```{r}
pos_week_pl <- ggplot(mapping = aes(x = week, y = n)) +
  facet_wrap(~ class) +
  geom_bar(data = df_pos, mapping = aes(fill = variable),
           stat = "identity", position = "stack") +
  geom_text(data = subset(df_pos, n > 0), mapping = aes(label = n), 
            size = 8 / cm(1), position = position_stack(vjust = 0.5), color = "white") +
  geom_text(
    data = data.frame(class = c("Class A", "Class B"), axis_title = c("Study week", "Study week")),
    mapping = aes(label = axis_title), hjust = 0.5, vjust = 3.5,
    x = min(df_pos$week) + diff(range(df_pos$week)) / 2,
    y = -Inf, color = 'black', size = 8 / cm(1)
  ) +
  scale_fill_manual(values = wes_palette("IsleofDogs1")) +
  scale_y_continuous(expand = expansion(add = c(0,1)), breaks = scales::breaks_width(2)) +
  scale_x_continuous(breaks = seq(1, 7, 1)) +
  labs(y = "Number of positive samples", x = "Study week", fill = "Virus") +
  theme_custom() +
  coord_cartesian(clip = "off") +
  theme(panel.grid = element_blank(),
        panel.spacing.x = unit(1, "cm"),
        axis.title.x = element_text(color = "white"),
        legend.position = "none",
        plot.title.position = "plot") +
  guides(fill = guide_legend(nrow = 1))

pos_week_pl
```

```{r}
# positive samples by study condition
df_pos_stud <- df_pos %>%
  group_by(aircleaner) %>%
  summarize(n = sum(n)) %>%
  ungroup() %>%
  mutate(aircleaner = factor(aircleaner, levels = c("No", "Yes")))

pos_cond_pl <- ggplot(mapping = aes(x = aircleaner, y = n, fill = aircleaner)) +
  geom_bar(data = df_pos_stud, stat = "identity", position = "stack", color = "black") +
  geom_text(data = subset(df_pos_stud, n != 0), mapping = aes(label = n), 
            size = 8 / cm(1), vjust = -1) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
  scale_fill_manual(values = wes_palette("Royal1")[1:2]) +
  labs(y = "Number of positive samples", x = "Air cleaner", fill = "Virus", title = "a") +
  theme_custom() +
  theme(panel.grid = element_blank(),
        plot.title.position = "plot",
        legend.position = "top",
        legend.title = element_blank(),
        legend.key.width = unit(.3, "cm"),
        legend.key.height = unit(.1, "cm")) +
  guides(fill = guide_legend(nrow = 1))

pos_cond_pl

save_plot(pos_cond_pl, 
          "../results/mol-data/saliva-by-study-condition.pdf",
          "../results/mol-data/saliva-by-study-condition.eps",
          w = 8, h = 8)
```

@@

pos_tot_pl <- ggplot(mapping = aes(y = n, x = 1, fill = variable)) +
  geom_bar(data = df_pos_tot, stat = "identity", position = position_stack(reverse = T)) +
  geom_text(data = subset(df_pos_tot, n != 0), mapping = aes(label = n), 
            size = 8 / cm(1), position = position_stack(vjust = 0.5, reverse = T), color = "white") +
  scale_fill_manual(values = wes_palette("IsleofDogs1")) +
  scale_y_continuous(expand = c(0,0)) +
  scale_x_continuous(expand = expansion(mult = c(0.05,0))) +
  coord_flip() +
  labs(y = "Number of positive samples", fill = "Virus", title = "a") +
  theme_custom() +
  theme(panel.grid = element_blank(),
        plot.title.position = "plot",
        legend.position = "top",
        legend.title = element_blank(),
        legend.key.width = unit(.3, "cm"),
        legend.key.height = unit(.1, "cm"),
        axis.title.y = element_blank(),
        axis.line.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  guides(fill = guide_legend(nrow = 1))

pos_tot_pl

save_plot(pos_tot_pl, 
          "../results/mol-data/saliva-distribution.pdf",
          "../results/mol-data/saliva-distribution.eps",
          w = 16, h = 3.5)
```

<!-- ```{r} -->
<!-- # combine -->
<!-- descr <- pos_tot_pl + plot_spacer() + pos_cond_pl & theme(legend.position = "bottom", legend.key.height = unit(.1, "cm"), -->
<!--                                           legend.key.width = unit(.3, "cm")) -->
<!-- descr <- descr + plot_layout(guides = "collect", widths = c(9.5, 1, 5.5), ncol = 2)  -->
<!-- descr <- descr + pos_week_pl  -->
<!-- descr <- descr + plot_layout(nrow = 2, heights = c(8, 8), design = 'ABC -->
<!--                              DDD') -->
<!-- save_plot(descr, pdf_file = "../results/mol-data/descriptives.pdf", eps_file = "../results/mol-data/descriptives.eps", h = 16, w = 16) -->
<!-- # saveRDS(pos_tot_pl + ggtitle(""), file = "../results/mol-data/descriptives-total.rds") -->
<!-- # saveRDS(pos_cond_pl + ggtitle(""), file = "../results/mol-data/descriptives-cond.rds") -->
<!-- # saveRDS(pos_week_pl + ggtitle(""), file = "../results/mol-data/descriptives-week.rds") -->
<!-- ``` -->

@@

tnet_pl <- tnet %>%
  mutate(type = factor("Saliva", levels = c("Saliva", "Air", "Filter"))) %>%
  ggplot(aes(y = date_infection, x = virus, size = n, shape = type)) +
  facet_wrap(~ class, ncol = 2, scales = "free_x") +
  ggh4x::facetted_pos_scales(x = mirror_scales) +
  geom_point(data = air_samples %>% 
               mutate(date_infection = as.POSIXct(paste0(date, "00:00:00", format = "%d-%m-%Y %H:%M:%S")),
                      n = factor(1, levels = c(1,2,3)),
                      class = factor(paste("Class", class), levels = c("Class A", "Class B")),
                      type = factor(type, levels = c("Saliva", "Air", "Filter")),
                      virus = factor(virus, levels = c("Flu B", "HRV", "AdV", "CoV", "MPV", "PIV"))),
             mapping = aes(color = virus), fill = "white",
             position = position_dodge(width = -.6, preserve = "single")) +
  geom_point(mapping = aes(fill = virus), color = "black") +
  geom_segment(aes(y = from, yend = to, xend = virus), size = 1,
              arrow = arrow(length = unit(0.2, "cm")), color = "black") +
  labs(size = "Number of infections", fill = "Virus", shape = "", title = "b") +
  coord_y_datetime(ylim = c(max(tnet$date_infection), min(tnet$date_infection))) +
  scale_y_datetime(date_breaks = "1 week", date_labels = "%b %d") +
  scale_size_discrete(range = c(4,8)) +
  scale_fill_manual(values = wes_palette("IsleofDogs1")) +
  scale_color_manual(values = wes_palette("IsleofDogs1")) +
  scale_shape_manual(values = c("Saliva" = 21, "Air" = 22, "Filter" = 23),
                     breaks = c("Saliva", "Air", "Filter")) +
  theme_custom() +
  theme(legend.position = "top",
        legend.direction = "horizontal",
        legend.box = "horizontal",
        plot.title.position = "plot",
        axis.title = element_blank(),
        #axis.text.x = element_blank(),
        #axis.ticks.x = element_blank(),
        panel.spacing = unit(1, "cm"),
        panel.grid.major.x = element_line(),
        panel.grid.minor.y = element_blank(),
        strip.text.x = element_text(size = 10, margin = margin(b = 10))) +
  guides(fill = "none",
         color = "none",
         shape = guide_legend(order = 1),
         size = guide_legend(nrow = 1, order = 2))

save_plot(tnet_pl, 
          pdf_file = "../results/mol-data/network-plot.pdf", 
          eps_file = "../results/mol-data/network-plot.eps", 
          w = 16, h = 16.5)
```
